\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Grammar fix.

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The ``NEW'' interface checks the local machine for if a proxy configured,
		and informs the user if the proxy is required, and if so, what those settings are (P).'' }
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
		and informs the user whether a proxy is required, and if so, what those settings are (P).}
\end{figure*}
